Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-04 demystify.tex
updates

However, not getting an interview typically means you do not get directly RA support (\autoref{sec:funding}) by an individual faculty (if they want to pay you to do research for them, then likely they want to talk to you first).  In this case, your application will be reviewed by the adcom and they will make a decision based on your application.

@@

In short, you should not worry too much about the timeline. Also do not send emails asking about interviews or status.

@@

You can also send an email to ask about the status of your application if you have received offers from other schools and need to make a decision soon. See \autoref{sec:accept-postpone-decline} for how to accept/postpone/decline offers.
% \section{Preparing and Tracking Applications}

@@

Students, especially international ones, often get confused on what to do after they get an offer from a professor, e.g., is it OK to postpone or accept/reject offers, and most importantly, how to do so without offending anyone. Many wonder about accepting an offer and then later rejecting it.  This section provides some guidance on these issues.

@@

\paragraph{Postponing an offer} If you need more time to decide, you can ask for more time: \emph{``Thank you for the offer.  I am very excited about it.  However, I am still waiting for other offers and need more time to decide.  Would it be possible to postpone the decision for a few weeks?''}.  This is perfectly fine and professors will understand and might even appreciate your honesty.  They will likely give you a few weeks to decide.  If you need more time, you can ask for more time.  But do not ask for too much time, e.g., more than a month.  You also should not postpone the offers multiple times, which will annoy people.

>>>>

However, no interviews typically means that you will not likely get an RA (\autoref{sec:funding}), which is offered by an individual faculty (if they want to pay you to do research for them, then likely they want to talk to you first).  In this case, your application (and TA/fellowship funding) will be reviewed and decided by the adcom.

You can also send an email to ask about the status of your application if you have received offers from other schools and need to make a decision soon. See \autoref{sec:accept-postpone-decline} for how to accept/postpone/decline offers.

@@

In short, you should not worry too much about the timeline. Also do not send emails asking about interviews or status (unless you have interviewed specifically with someone then you can ask that person for status updates and others \autoref{sec:accept-postpone-decline}).

@@

% \section{Preparing and Tracking Applications}

@@

Students, especially international ones, often get confused on what to do after they get an offer from a professor, e.g., is it OK to postpone or accept/reject offers?, and most importantly, how to do so without offending anyone. Many also wonder about accepting an offer and then later rejecting it.

@@

\paragraph{Postponing an offer} If you need more time to decide, you can ask for more time: \emph{``Thank you for the offer.  I am very excited about it.  However, I am still waiting for other offers and need more time to decide.  Would it be possible to postpone the decision for a few weeks?''}.  This is perfectly fine and professors will understand and might even appreciate your honesty.  They will likely give you a few weeks to decide.  If you need more time, you can ask for more time.  But do not ask for too much time, e.g., more than a month.  You also should not postpone the offer multiple times, which will annoy people.
